Notes on Twisted SYM

### 2019-01-09 10-9-8d_twists_1_19.tex
some more 8d edits

>>>>

If we assume these R-symmetry weights are correct then, indeed, the holomorphically twisted theory is equivalent to the cotangent theory to $\bun_G(X^4)$ as predicted.  Question: I'm not sure how to see this in the BRST language.  I can verify this using the BV action functional: it gives the twisted BV complex an $L_\infty$ structure which is equivalent to the one on that cotangent theory.  For instance, the quadratic term $B^{10} \wedge \ol \dd A^{10}_{0,1}$ in the BV action gives us the differentials $\phi \to A$ and $A' \to B$.
